Refractory anaphylaxis: Data from the European Anaphylaxis Registry

### 2019-08-21 analysis/paper/paper.Rmd
add pval, change line 119

`r elicitorTab[1,8]`% of food elicited refractory cases had a previously confirmed diagnosis of food allergy. Severe cases of anaphylaxis were most frequently elicited by insects and food triggers.
Insect-venom-elicited, refractory cases were significantly less often elicited by yellow-jacket-stings (but not by bee-stings) than severe, non-refractory cases (table \@ref(tab:elicitExact)).

@@

```{r elicitorTab}
knitr::kable(elicitorTab[,c(0,1,5,6,7,8,2,3,4)+1], caption = "Summary of elicitors in the refractory anaphylaxis cases and severe, non-refractory anaphylaxis cases as a control. ANA - anaphylaxis, Age is represented as a mean, p-value derived from the Fisher's exact test.",
             #col.names = c("n","Age","Male sex [%]","Perioperative [%]","Food allergy [%]","refractory ANA [%]","severe ANA [%]","p value")
              align = rep("r",10),
             nsmall=2)
            #digits = 1,
             # align = rep("r",10),
             # trim=T,
             # scientific=F,
             # nsmall=3,
             #drop0trailing = F

>>>>

`r elicitorTab[1,9]`% of food elicited refractory cases had a previously confirmed diagnosis of food allergy. Severe cases of anaphylaxis were most frequently elicited by insects and food triggers.
Refractory anaphylaxis cases elicited by insects were more often elicited by bees than severe, non-refractory cases, p = `r table(data3$q_340_insects,data3$rANA) %>%  {rbind(addmargins(.[3:8,],1) %>% tail(1),.[2,])} %>% as.matrix() %>% fisher.test() %>% {.$p.value} %>% round(4)` (table \@ref(tab:elicitExact)).

@@

```{r elicitorTab}
knitr::kable(elicitorTab#[,c(0,1,5,6,7,8,2,3,4)+1]
             , caption = "Summary of elicitors in the refractory anaphylaxis cases and severe, non-refractory anaphylaxis cases as a control. ANA - anaphylaxis, Age is represented as a mean, p-value derived from the Fisher's exact test.",
             #col.names = c("n","Age","Male sex [%]","Perioperative [%]","Food allergy [%]","refractory ANA [%]","severe ANA [%]","p value")
              align = rep("r",10),
             nsmall=2)
            #digits = 1,
             # align = rep("r",10),
             # trim=T,
             # scientific=F,
             # nsmall=3,
             #drop0trailing = F
